---
title: "Super Cool Penguins"
author: "Ben Kleinman"
date: "`r Sys.Date()`"
output: 
  md_document
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F)
library(prettydoc)
# Note you might have to install prettydoc
# install.packages("prettydoc")
```

## R Markdown
Here we are going to learn a bit about penguins

## Penguins
See below for averages on penguins. 

```{r penguins-ex, echo=FALSE}
library(dplyr)
library(palmerpenguins)

data("penguins")

penguins_sex <- group_by(.data = penguins, sex)
penguins_sex_adelie <- filter(.data = penguins_sex, species == "Adelie")

summarize(
  .data = penguins_sex_adelie,
  avg_bill = mean(bill_length_mm, na.rm = TRUE), avg_mass = mean(body_mass_g, na.rm = TRUE))
```


## The Penguins of Torgersen 
The following tracks the change in average body mass and bill length measured for the penguins of Torgersen from 2007 to 2009.

```{r}
penguins %>%
  filter(island == 	"Torgersen") %>%
  group_by(year) %>%
  summarize(body_mass = mean(body_mass_g, na.rm = TRUE)) 

```
```{r}
penguins %>%
  filter(island == 	"Torgersen") %>%
  group_by(year) %>%
  summarize(ave_bill_lenght = mean(bill_length_mm, na.rm = TRUE)) 

```


# Final task

You need to make a README.md doc -- practice by outputting a .md file here and renaming it to README.md before pushing to github
